The proposed system is a practical way of distributing large files anonymously 
among peers on the internet. It is easy for everyone to join the network: it 
does not come with any associated cost, and transfers are not a considerable 
inconvenience for the 3rd party nodes.

The only downside is the fact that the nodes in the network which are not 
actively transferring will occasionally have to donate a part of their 
bandwidth. The users could configure a bandwidth limit amount in such a way as 
to not negatively impact their internet usage. Other data that is not big, but 
should be mentioned, is the frequent background traffic required for node 
discovery messages and forwarding search requests and replies. An upcoming 
version of this paper will be released, in which this background traffic and 
passive transfer assistance are measured in a simulation.

Another downside is the fact that a file cannot be downloaded from multiple 
sources at a time, similar to BitTorrent, to reduce traffic for individual file 
distributors and increase transfer speeds. A future version of the protocol 
might include this functionality.

SAND could work really well is low to mid income countries where piracy and 
cheap high-speed internet broadband are common, like in Romania for example. As 
a side note, in Romania, these circumstances allowed for many citizens to 
acquire technical skills and be lifted out of poverty while the country is now 
one of the leadings in technology workers per capita \cite{romaniasoftwaredev}.

Clandestine software and specialty literature usage without legal consequences 
may effectively aid people in other underdeveloped countries, like those in 
Africa. We could consider this as a means of the western world to pay back a 
bit for the continuing neocolonialist practices.
